Deciding Bitvector Termination with Program Synthesis

### 2014-07-05 papers/termination/paper.tex
"We enumerate programs startign with the shortest"

\subsection{Genetic Programming and Incremental Evolution} \label{sec:gp}
To generate candidate (non-)termination proofs in the synthesise phase of the refinement loop,
we make use of genetic programming (GP) \cite{langdon:fogp} as an alternative to model checking and exhaustive search.  
Genetic programming provides an intelligent and adaptive way of searching through the space of computer programs
for an individual that is highly fit in solving the problem at hand
by using the Darwinian principle of survival and reproduction of the fittest.
Thus, the program that emerges from the genetic programming paradigm is a consequence of fitness.

>>>>

\subsection{Candidate Generation Strategies}
\noindent{\bf Explicit Proof Search} The simplest strategy for finding candidates
is to just exhaustively enumerate them all, starting with the shortest and
progressively increasing the number of instructions.  Since the set of
$\mathcal{L}$-programs is recursively enumerable, this procedure is complete.
\\

\noindent {\bf Genetic Programming and Incremental Evolution} \label{sec:gp}
To generate candidate (non-)termination proofs in the synthesise phase of the refinement loop,
we make use of genetic programming (GP) \cite{langdon:fogp} as an alternative to model checking and exhaustive search.  
Genetic programming provides an intelligent and adaptive way of searching through the space of computer programs
for an individual that is highly fit in solving the problem at hand
by using the Darwinian principle of survival and reproduction of the fittest.
Thus, the program that emerges from the genetic programming paradigm is a consequence of fitness.
